\section{PROBLEM FORMULATION}

We study motion planning for a single holonomic robot operating in a two-dimensional discrete grid. The objective is to synthesize a collision-free trajectory from a known start position to a fixed goal while both static and dynamic obstacles may be present. Unlike classical formulations that assume a static environment, we explicitly allow obstacles to move over time and require the planner to account for this evolution when producing a feasible path.

\subsection{General Assumptions}
\begin{itemize}
	\item The environment is a discrete gridworld (discrete space and discrete time).
	\item The robot is holonomic with deterministic dynamics and is modeled as a point mass.
	\item The initial robot state and the goal state are known and fixed.
	\item The number of obstacles and their initial positions are known.
	\item The robot state is observable at every time step.
	\item The robot is equipped with a local sensor that yields a $5 \times 5$ occupancy grid centered on the robot (local observation of nearby cells).
\end{itemize}

\subsection{Mathematical Model}
The planning problem is defined on the following spaces:
\begin{align*}
	\text{State space:}\quad & S = \{(x,y) \mid x,y \in \mathbb{N},\ 0 \leq x \leq X_{\text{dim}},\ 0 \leq y \leq Y_{\text{dim}}\} \subset \mathbb{N}^2, \\
	\text{Action space:}\quad & A = \{(0,1),\ (0,-1),\ (-1,0),\ (1,0),\ (0,0)\} \subset \mathbb{Z}^2, \\
	\text{Observation space:}\quad & G \in [0,1]^{5 \times 5}, \\
	\text{Static obstacles:}\quad & O \subset S.
\end{align*}

The robot dynamics are given by a deterministic transition function
\begin{equation*}
	f : S \times A \rightarrow S,
\end{equation*}
which maps the current state and chosen action to the next state. Dynamic obstacles
evolve over time; let $M_i \subset S$ denote the set of moving obstacle states at
discrete time index $i \in \{0,\dots, N-1\}$ for a planning horizon of length $N$.

\subsection{Planning Objective}
We seek a trajectory $T = \{S_0, S_1, \dots, S_{N-1}\}$ such that $S_0$ is the known
initial state and $S_{N-1}$ coincides with the goal state. The trajectory is feasible if
for every $i \in \{0,\dots, N-2\}$ there exists an action $a \in A$ satisfying
\begin{equation*}
	f(S_i, a) = S_{i+1}, \qquad S_i \notin O, \qquad S_i \notin M_i.
\end{equation*}
The task is to compute at least one such collision-free trajectory that respects both static and time-varying obstacle sets under the stated assumptions.
